\documentclass[class=report, crop=false]{standalone}
\usepackage{import}

\begin{document}

\chapter{Related Works}\label{cha:related-works}
\pagestyle{scrheadings}
In this chapter we list a few related platforms that are similar in price, hardware and software to ours. This list is not exhaustive and serves only as a base of comparison.


\section{Turtlebot 3 Burger}\label{sec:turtlebot3burger}
One of the most popular ROS platforms similar to ours is the Turtlebot 3 Burger\footnotemark. It is similarly equipped with a Raspberry Pi 3, 3-Axis accelerometer, 3-Axis gyroscope, 3-Axis magnetometer.

It also has Dynamixel actuators with magnetic contactless rotary encoders, a custom OpenCR control board with an ARM Cortex-M7 which is compatible with the Arduino software development environment and a 360 degree LiDAR for simultaneous localization and mapping(SLAM).
The platform is modular, extensible and it is open source software and hardware for 549\$\cite{turtlebot3}.

\footnotetext{http://www.robotis.us/turtlebot-3/}

\section{Wolfbot}\label{sec:wolfbot}
The Wolfbot\cite{wolfbot} platform is built around the Beaglebone Black, which has a ARM Cortex A8 1GHz processor. Its focus is on environmental sensing with a SensorDrone module with low and high power communication(ZigBee and WiFi). It is also equipped with an omidirectional wheel, a 3D accelerometer with a magnetometer, infrared distance sensor(IR) and a 720p camera with a microphone. It utilizes SLAM through the IR sensor and provides a software interface for OptiTrack Tracking tools for a more accurate visual SLAM.

The electrical layout of the platform consists of multiple PCBs and a 5200mAh battery for long and reliable operation. It lasts around 8.72 hours with a constant medium load. The total bill of materials(BOM) is under 550\$.

\section{JetBot}\label{sec:jetbot}
The JetBot\footnotemark is an open source autonomous robotics kit that provides a low cost deep learning capable robot with the Jetson Nano Developer Kit from Nvidia for around 250\$.


The Jetson Nano compute module is a system on a module(SOM) equipped with an ARM A57 processor, an Nvidia Maxwell 128 core GPU and 4GBs of RAM. The provided operation system(OS), JetPack, is an Ubuntu 18.04 based Linux environment with support for many CUDA accelerated libraries. Preliminary research\cite{hubbard2019} on harnessing the GPU for Neural Networks is promising.

The JetBot itself includes an IMX219 8MP camera, 3D-printable chassis, battery pack, motors, $ I^2C $ motor driver.\footnote{https://github.com/NVIDIA-AI-IOT/jetbot/wiki/bill-of-materials}

The platform supports ROS melodic for easy integration with already existing robotic software and developing SLAM methods.

\footnotetext{http://www.devblogs.nvidia.com/jetson-nano-ai-computing/}

\end{document}
